Continous occlusion models and traffic scene understanding

### 2015-05-04 CVPR/Source/experiments.tex
Latest version of presentation.

\paragraph{Dataset}

@@

Using both the evidence terms we can write probability of association as
\begin{align}
  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
  \label{eq:prob-assoc}
\end{align}

@@

>>>>

\paragraph{Dataset} We use KITTI dataset for our experiments.  \cite{geiger2013vision}. KITTI dataset is a labeled video sequence of road scenes under variety of driving conditions including highways and residential areas in Karlsruhe, Germany. It provides manually labelled ground truth data for localization of cars and also uses velodyne data provide metrically accurate estimates of cars location.

@@

Using both the evidence terms we can write probability of association as
\begin{align}
  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \exp(-\Ereproj(\lambda))d\lambda
  \label{eq:prob-assoc}
\end{align}

@@

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Algorithm & Total & Unoccluded cars & Occluded cars \\
    \midrule
    bounding box only & 0.21 & \textbf{0.03}  & 0.36\\
    Using $P^{(ij)}_{\text{assoc}}$ & \textbf{0.21} & 0.08 & \textbf{0.32}\\
    Using $\assocP{}$ & 0.23 & 0.09 & 0.34 \\
    Using $P^{(ij)}_{\text{assoc by reproj}}$ & 0.23 & 0.08 & 0.34\\
    \bottomrule
  \end{tabular}
  \caption{Association Experiment results. The error is in terms of fraction of points wrongly associated with objects, hence lower is better.}
\end{table}

\paragraph{Localization Experiment}
Localization is the main goal of our project. We estimate the position, orientation and dimensions of the car with our framework and compute the error in birds eye view domain along the ground plane. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.

% %\subsection{Qualitative Results}
% \begin{figure}
%         \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000061.png}
% \end{figure}
% \begin{figure}
%   \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_lane_size_bboxOcc_yawTstepWiseInference/0000000061.png}
% \end{figure}
% \begin{figure}
%   \includegraphics[width=\columnwidth]{results/Visualization/City/2011_09_26_drive_0009/single_window_contPtTracks_size_bboxOcc_yawTstepWiseInference/0000000063.png}
% \end{figure}

%\subsection{Quantitative results}

\begin{table}
  \centering
  \begin{tabular}{lrrr}
    \toprule
    Energy & t & yaw & dim \\
    \midrule
    lane+contPtTracksNoOcc+size+bbox+posT   & 3.80 & 0.91 & 1.58 \\
    lane+contPtTracks+size+bboxOcc+posT+col & \textbf{3.78} & 0.91 & 1.58 \\
    lane+contPtTracks+size+bboxOcc+posT     & 3.81 & 0.92 & 1.59 \\
    lane+size+bboxOcc+posT+col              & 3.92 & 0.91 & 1.15 \\
    lane+size+bboxOcc+posT                  & 3.83 & 0.90 & 1.14 \\
    lane+size+bbox+posT                     & 3.83 & 0.90 & \textbf{1.14} \\
    initialization                          & 3.79 & \textbf{0.86} & 1.64 \\
    \bottomrule
  \end{tabular}
  \caption{Localization experiment results with different combination of energies. We report error in three metrics translation error (t) in meters per car, yaw error (yaw) in radians per car and dimension error is again meters per car.}
\end{table}

### 2015-05-04 CVPR/Source/localize.tex
Added poster and a lots of tikz figures.
Latest version of presentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Continuous Energies for Object Localization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We explain energies in this section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}
We model continuous point tracks energy with explicit occlusion reasoning as
the expected re-projection error over the association probability,

\begin{multline}
  \Energy{traci}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = \\
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $\assocP$ is the association probability of
$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$
and $\Ereproj(\lambda)$ is the re-projection error given by
%
\begin{align}
  \assocP &= \Prefl\Ptrans\\
  \Ereproj(\lambda) &= \left\|\trackpj{t+1} - \projectionOft{\invProjectionOf{\trackpj{t}, \lambda}}\right\|^2 .
  \label{eq:reprojerror}
\end{align}

The  $\projectionOf{.}$ and $\invProjectionOf{.}$ denote the projection and
inverse projection functions that project 3D point to camera image and vice
versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t$ while the projection depends on pose at time $t+1$ which can be different.

\begin{comment}
  \subsubsection{Occupancy function}
  Assuming occupancy to be a
  probability distribution over 3D space. For each TP the
  occupancy is modeled as a logistic function 
  \begin{align}
     \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
  \end{align}
  where $L(.)$ is the logistic function defined by
  \begin{align}
    L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
      1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
      }
  \end{align}
  where $d(\mathbf{x},\pos{i}{t-1}) =
  (\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
  10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
  0.9$
  % Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
  % reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
  % $\lambda$. Let
\end{comment}

\begin{comment}
  \subsubsection{Approximations}
  Reflection probability of $i$th TP is easy to compute
  analytically 
  \begin{multline}
    \Prefl =
    (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
    = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
    \label{eq:analytic-prefl}
  \end{multline}
  where 
  \begin{multline}
    \nabla \occfxi^\top\ray \\=
    \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
  \end{multline}
  where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
  from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.

  However, the transmission probability needs to be approximated.  
  %
  % \subsubsection{Computing $\Prefl$ and $\Ptrans$}
  % Focusing on  $\nabla \occfxi$ 
  % 
  % \begin{multline}
  %   \nabla \occfxi =\\
  %   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
  %     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
  %   } \\ 
  %   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
  %   \pos{i}{t-1}))\right)
  %   \\
  %   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
  % \end{multline}
  % where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
  % from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
  % Focusing on $\nabla d(.)$
  % 
  % \begin{align}
  %   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
  % \end{align}
  % Back to \eqref{eq:analytic-prefl}
  % 
  % \begin{multline}
  %   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
  %   \sech^4\left(\frac{k}{2}\dishort\right) 
  %   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
  % \end{multline}
  % 
  % The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
  % $\nabla k\dishort$ projected in the ray direction $\ray$.
  % 
  % \begin{align}
  %   \Ptrans = 
  %   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
  % \end{align}
  % \begin{multline}
  % \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
  % =  \\
  % \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
  % \end{multline}
  % 
  % The above integral is very difficult to approximate or compute analytically.
  So based on intuition, we approximate the $\Ptrans$ by following function
  \begin{align}
  \label{eq:evalCumulativePtrans}
    \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
    L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
      1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
      \mu^i_u))}
    }
    \\
    L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
    1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
  }
  \end{align}
  where 
  \begin{align}
    \mu_u^i &= \projectionOf{\pos{i}{t-1}} \label{eq:muiudef}\\
    \Sigma_u^i &= \projectionOf{\Sigma_i} \label{eq:sigmauidef}\\
    \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
    k_u &= 10\log(49)\\
    k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
    \label{eq:ptransmissionInit}
  \end{align}
  is the distance of the centre of the TP from the camera.

@@

\subsection{Object detection energy with occlusion}

@@

\subsubsection{Detection scores with occlusion reasoning} 
With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
compute the probability of a point $\mathbf{u}$ on image be occluded assuming
the point is on TP $i$ with mean depth $\mu^{(i)}_d$ as
\begin{align}
  O_{i}(\mathbf{u}, \mu^{(i)}_d) = 1 - \Ptransmud \enspace .
\end{align}

If we a portion of our proposed detection bounding box is known to be occluded,
then we would like to decrease the confidence in the detection score about the
localization of that end of the object. Assuming that the occlusion is often on
the boundary of detection bounding boxes, we want to decrease our confidence on
the mean detection boundaries around the occluded boundaries. 
One of the simplest ways will be to scale the appropriate diagonal element of
$\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
does not model appropriate how does occlusion affects the non diagonal terms.
Hence, we choose a covariance addition model where we compute a occlusion
covariance matrix, that provides a measure of occlusion in each direction.

To re-model our detection scores scaled by continuous occlusion we sample
$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
GMM $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
%
\begin{align}
  \Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j
\end{align}
%
The detection scores GMM with occlusion is given by replacing the covariance
matrix
%
\begin{multline}
  S'(\bb{i}) =\\
  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{multline}

@@

\subsection{Lane energy}
\label{sec:laneEnergy}
 The lanes are modeled as splines. Here we assume that the confidence in lane
 detection is decreases as the distance from the lane center increases.  The
 energy is given by the dot product between car orientation and tangent to the
 lane at that point.

\begin{multline}
  \label{eq:laneOrientationEnergy}
  \Energy{lane} = \\
  \sum_{m \in M_{\text{close}}}
  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
\LaneUncertainty{\pos{i}{t}}
\end{multline}
where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < 50\} $ is
the set of nearby lanes and 
\begin{multline}
\LaneUncertainty{\pos{i}{t}} = \\
  \frac{1}{1 + exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
\end{multline}
for some constant $w_{\text{road}}$ that represents the width of the road.

\subsection{Transition probability}
Dynamics constraints should not only enforce smooth trajectories, but also the
holonomic constraints.  The following energy adds a penalty if the change in
position is not in direction of previous orientation.

@@

\subsection{Collision energy}

@@

\begin{multline}
  \label{eq:collisionEnergyHellingerDistance}
  \EnergyCol =\\ -\log\left(
  A_{ij}
  e^{-\frac{1}{8}
    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
    P^{-1}
    \left(\pos{i}{t} - \pos{j}{t}\right)
    }
    \right)
\end{multline}
where 
\begin{align}
  A_{ij} &= \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}
  {|P|^\frac{1}{2}}\\
  P &= \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j\\
\Sigma_i^{-1} &= R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l_i & 0 \\ 0 & 2/w_i \end{bmatrix}
R_{\ori{i}{t}}
\end{align}

\subsection{Size Prior}

@@

\begin{align}
  \label{eq:totalSizeEnergy}
  \Energy{prior} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
  \expDimsn)
\end{align}

>>>>

With the understanding of our occlusion aware 3D representation of objects, we are know in position to describe the energies that we defined in Chapter~\ref{sec:setup}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}
We model continuous point tracks energy with explicit occlusion reasoning as
the expected re-projection error over the association probability,

\begin{align}
  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{align}
where $\assocP$ is the association probability of
$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$, $\{ \relp{i}{t} \}_i$ are the poses of all occluding objects at time $t$, $ \{ \dimsn{i} \}_i$ are the dimensions of all objects that occlude $i$
and $\Ereproj(\lambda)$ is the re-projection error given by
%
\begin{align}
  \assocP &= \Prefl\Ptrans\\
  \Ereproj(\lambda) &= \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2 .
  \label{eq:reprojerror}
\end{align}

The  $\projectionOf{.}$ and $\invProjectionOftm{.}$ denote the projection and
inverse projection functions that project 3D point to camera image and vice
versa. Note that inverse projection $\invProjectionOf{.}$ depend on both the
point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on TP pose at time $t-1$ while the projection depends on pose at time $t$ which can be different.

\begin{comment}
  \subsection{Occupancy function}
  Assuming occupancy to be a
  probability distribution over 3D space. For each TP the
  occupancy is modeled as a logistic function 
  \begin{align}
     \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
  \end{align}
  where $L(.)$ is the logistic function defined by
  \begin{align}
    L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i) = \frac{1}{
      1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t-1}))}
      }
  \end{align}
  where $d(\mathbf{x},\pos{i}{t-1}) =
  (\mathbf{x}-\pos{i}{t-1})^\top\Sigma_i(\mathbf{x}-\pos{i}{t-1})$ and $k =
  10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
  0.9$
  % Once we have our distribution over $\lambda$, $\lambdadist$ we can compute the
  % reprojection of $\trackpj{t-1}$ over image in time $t$ as a function of
  % $\lambda$. Let
\end{comment}

\begin{comment}
  \subsection{Approximations}
  Reflection probability of $i$th TP is easy to compute
  analytically 
  \begin{multline}
    \Prefl =
    (\max \{ 0, \nabla \occf^\top \ray \})^2 \\
    = (\max \{ 0, \nabla \occfxi^\top\ray \})^2
    \label{eq:analytic-prefl}
  \end{multline}
  where 
  \begin{multline}
    \nabla \occfxi^\top\ray \\=
    \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
  \end{multline}
  where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
  from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.

  However, the transmission probability needs to be approximated.  
  %
  % \subsection{Computing $\Prefl$ and $\Ptrans$}
  % Focusing on  $\nabla \occfxi$ 
  % 
  % \begin{multline}
  %   \nabla \occfxi =\\
  %   \frac{-k\nabla d(\mathbf{x}, \pos{i}{t-1})e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))}}{
  %     (1 + e^{-k(1-d(\mathbf{x}, \pos{i}{t-1}))})^2
  %   } \\ 
  %   = -k\nabla d(\mathbf{x}, \pos{i}{t-1})\sech^2\left(\frac{k}{2}(1-d(\mathbf{x},
  %   \pos{i}{t-1}))\right)
  %   \\
  %   = \nabla k\dishort \sech^2\left(\frac{k}{2}\dishort\right)
  % \end{multline}
  % where $\dishort = 1-d(\mathbf{x}, \pos{i}{t-1})$ is a signed distance measure
  % from the contour of the ellipsoid where $d(\mathbf{x}, \pos{i}{t-1})$ is 1.
  % Focusing on $\nabla d(.)$
  % 
  % \begin{align}
  %   \nabla d(\mathbf{x}, \pos{i}{t-1}) = 2\Sigma_i(\mathbf{x} - \pos{i}{t-1})
  % \end{align}
  % Back to \eqref{eq:analytic-prefl}
  % 
  % \begin{multline}
  %   (\max \{ 0, \nabla \occf^\top \ray \})^2 = \\
  %   \sech^4\left(\frac{k}{2}\dishort\right) 
  %   (\max \{ 0 , \nabla k\dishort^\top\ray\})^2
  % \end{multline}
  % 
  % The probability is simply $\sech^2(.)$ scaled by gradient of ellipsoid
  % $\nabla k\dishort$ projected in the ray direction $\ray$.
  % 
  % \begin{align}
  %   \Ptrans = 
  %   e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
  % \end{align}
  % \begin{multline}
  % \int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}
  % =  \\
  % \int_{1}^{\lambda} \ln{\left(1 - \sum_i \occfi\right)}{d\lambda}
  % \end{multline}
  % 
  % The above integral is very difficult to approximate or compute analytically.
  So based on intuition, we approximate the $\Ptrans$ by following function
  \begin{align}
  \label{eq:evalCumulativePtrans}
    \Ptrans &= \prod_i L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)L_{\lambda}(\lambda; \mu^i_d)\\
    L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u) &= \frac{1}{
      1 + e^{-k_u(1 - (\mathbf{u} - \mu^i_u)^\top\Sigma^i_u(\mathbf{u} -
      \mu^i_u))}
    }
    \\
    L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d) &= \frac{1}{
    1 + e^{-k_d(\lambda - \mu^i_d(\mathbf{u}))}
  }
  \end{align}
  where 
  \begin{align}
    \mu_u^i &= \projectionOf{\pos{i}{t-1}} \label{eq:muiudef}\\
    \Sigma_u^i &= \projectionOf{\Sigma_i} \label{eq:sigmauidef}\\
    \mu^i_d(\mathbf{u}) &= \relp{i}{t}\\
    k_u &= 10\log(49)\\
    k_d &= \frac{\log(49)}{\sqrt{h^2 + l^2 + w^2}}
    \label{eq:ptransmissionInit}
  \end{align}
  is the distance of the centre of the TP from the camera.

@@

\section{Object detection energy with occlusion}

@@

\subsection{Detection scores with occlusion reasoning} 
With our model of $\Ptrans$ described in Section \ref{sec:TPmodel}, we can
compute the probability of a point $\mathbf{u}$ on image be occluded assuming
the point is on TP $i$ with mean depth $\mu^{(i)}_d$ as
\begin{align}
  O_{i}(\mathbf{u}, \mu^{(i)}_d) = 1 - \Ptransmud \enspace .
\end{align}

If we know a portion of our proposed detection bounding box is known to be
occluded, then we would like to decrease the confidence in the detection score
about the localization of that end of the object. Assuming that the occlusion
is often on the boundary of detection bounding boxes, we want to decrease our
confidence on the mean detection boundaries around the occluded boundaries.
One of the simplest ways will be to scale the appropriate diagonal element of
$\Sigma_j$ by an appropriate scaling factor proportional to occlusion. But this
does not model explain the affect of occlusion on the non diagonal terms.
Hence, we choose a covariance addition model where we compute a occlusion
covariance matrix, that provides a measure of occlusion in each direction.

To re-model our detection scores scaled by continuous occlusion we sample
$O_{i}(\mathbf{u}, \mu^{(i)}_d)$ at the hypothesized detection boundaries from
GMM $S(.)$ and we augment the detection boundary covariance matrix by
$\mathcal{P}_{j} = \rho_{j}\rho_{j}^\top$ where $\rho_{j} = O_{j}(\mathbf{u},
\mu^{(i)}_d)$. The new covariance matrix in detection score is given by 
%
\begin{align}
  \Sigma'^{(d)}_j = \mathcal{P}_{j} + \Sigma^{(d)}_j
\end{align}
%
The detection scores GMM with occlusion is given by replacing the covariance
matrix
%
\begin{align}
  S'(\bb{i}) =
  \sum_j A_j \exp(-(\bb{i}-\mu^{(d)}_j)^\top \Sigma'^{(d)-1}_j
  (\bb{i}-\mu^{(d)}_j))
\end{align}

@@

\section{Lane energy}
\label{sec:laneEnergy}
 The lanes are modeled as splines. Here we assume that the confidence in lane
 detection is decreases as the distance from the lane center increases.  The
 energy is given by the dot product between car orientation and tangent to the
 lane at that point.

\begin{align}
  \label{eq:laneOrientationEnergy}
  \Energy{lane} = 
  \sum_{m \in M_{\text{close}}}
  (1 - \ori{i}{t} \cdot \text{TAN}(L_{m}(k), \pos{i}{t}) )
\LaneUncertainty{\pos{i}{t}}
\end{align}
where $M_{\text{close}} = \{m : \text{DIST}(L_{m}(k), \pos{i}{t}) < d_{\text{thresh}}\} $ is
the set of nearby lanes close to the object by a certain distance threshold $d_{\text{thresh}}$ and 
\begin{align}
\LaneUncertainty{\pos{i}{t}} = 
  \frac{1}{1 + \exp(-q(w_{\text{road}} - \text{DIST}(L_{m}(k), \pos{i}{t})))}
\end{align}
for some constant $w_{\text{road}}$ that represents the width of the road.

\section{Transition probability}
Dynamics constraints should not only enforce smooth trajectories, but also the
holonomic constraints.  The following energy adds a penalty if the change in
position is not in direction of previous orientation.

@@

\section{Collision energy}

@@

\begin{align}
  \label{eq:collisionEnergyHellingerDistance}
  \EnergyCol =
  -\log\left(
  A_{ij}
  e^{-\frac{1}{8}
    \left(\pos{i}{t} - \pos{j}{t}\right)^\top
    P^{-1}
    \left(\pos{i}{t} - \pos{j}{t}\right)
    }
    \right)
\end{align}
where 
\begin{multline}
  A_{ij} = \frac{|\Sigma_i|^\frac{1}{4}|\Sigma_j|^\frac{1}{4}}{|P|^\frac{1}{2}}, \hfill
  P = \frac{1}{2}\Sigma_i + \frac{1}{2}\Sigma_j, \hfill
\Sigma_i^{-1} = R^\top_{\ori{i}{t}} \begin{bmatrix} 2/l_i & 0 \\ 0 & 2/w_i \end{bmatrix}
R_{\ori{i}{t}}
\end{multline}

\section{Size Prior}

@@

\begin{align}
  \label{eq:totalSizeEnergy}
  \Energy{size} &= (\dimsn{i} - \expDimsn)^\top\Sigma_{\expDimsn}^{-1}(\dimsn{i} -
  \expDimsn)
\end{align}
